\documentclass[11pt]{article}
\usepackage[papersize={5.5in,8.5in}]{geometry}
\usepackage{fontspec}
\usepackage{lettrine}
\newfontfamily{\sheikahfont}{BotW Sheikah}[Scale=MatchUppercase]
\newfontfamily{\gerudofont}{Gerudo's Typography}[Scale=MatchUppercase]
\newfontfamily{\ipafont}{Doulos SIL}[Scale=MatchUppercase]
\def\sheikah#1{{\sheikahfont #1}}
\def\gerudo#1{{\gerudofont #1}}
\def\ipa#1{{\ipafont #1}}
\begin{document}
\lettrine[lines=8]{L}{ong ago, when} the waters of the Lanay{\-}ru Seaway still reached all the way to Volefoel,\footnote{Recorded as the variant \gerudo{'olefoil} in mss. TK TK some fake manuscripts. The name itself is of obscure origin, perhaps Mogma.}
and the Great Raft of Floria still spilled its Great Florian floods across the south of Hyrule,
and Eldin Glacier was only a tiny rime of frost in the crater of that most ancient of volcanos,
there lived a Sheikah girl only slightly older than you are.

Her name was Prita,%
  \footnote{Alternatively, Pryta (\gerudo{Pryta})-- the name is given as \gerudo{Prita} in TK TK some made up manuscripts, \gerudo{Pryta} in TK TK some other made up manuscripts. Uncertain which is closer to the original, but given the \gerudo{i}-\gerudo{y} shift of late middle Gerudo, taking \gerudo{Prita} to be the original spelling.} 
and she lived in the crater, as all Sheikah did in those days (that is why we call them Sheikah),%
  \footnote{The Gerudo and Sheikah words for a small cave or grotto, \gerudo{ttei-a} (\ipa{t̪'eɪcə}) and \sheikah{cheika} (\thinspace{}\ipa{t͡ʃeɪkʰə}), respectively, from pre-Hylian \ipa{*θeɪkə}, form the root of the demonym Sheikah (\gerudo{avttei'a} and \sheikah{amcheika}, lit.~`grotto-dwellers') in both languages}
and she lived with her mother and her father (that is what Sheikah call their voe-mother) and her three aunts and her three uncles (that is what they call their voe-aunts), and five sisters and five brothers (that is what they call voe-sisters), and ever so many neighbors.

Now her father and mother and aunts and uncles had the certain and unwavering belief that, when the Chief of all Sheikah decided he was tired of being chief, it would be her father's turn to be Chief of all Sheikah, and that when \emph{he} was tired, it would be one her brother's turns -- which, though it may seem strange, is a very common way of picking chiefs in many far off places -- but it was their nearest neighbors' and their nearest neighbor father's and nearest neighbor mother's and nearest neighbor aunts' and uncles' sure and unshakeable belief that their nearest neighbor father ought to be chief of all Sheikah next, and when he was done that one of their nearest neighbor voe children should take a turn. And her family and her nearest neighbors' family quarreled and quibbled, and spat and squabbled, and fought and feuded over the chiefdom.

In the dry season, when it was time to gather the ground-apples, the daisy roots, and all the thousand varieties of legumes that they grow in the mountains, her family and her nearest neighbors could not work their nearest-neighboring terrace plots without arguing and shouting. So when her nearest neighbors gathered from their terrace plots on the east side of the mountain, she and all her family would hike far across the mountain's peak and gather from their own terrace plots on the west side of the mountain; when her nearest neighbors worked their terrace plots on the west side, she and her family would gather from their own terrace plots on the east; and both families asked the rest of their ever so many neighbors not to ask them to work the terrace plots held in common on the same day. 

And In the wet season, when it was time to plant, her family would hurry out to one side of the mountain and her nearest-neighbors would hurry out to the other and then as soon as they were done with their planting -- which they worked through quickly, because it was so wet and rainy -- they would go home and each family would sit at the tiny windows of their house, making masks, sewing shawls, simmering stews, working at all their several chores, and glare out at the other family's hut.

The two families continued on like this for four whole years until the rest of their ever so many neighbors came together and informed them that their quarrels and quibbles, and spats and squabbles, and fights and feuds were intolerably ridiculous, and that if neither family could not decide which family's father was to be chief, and who would follow him, all their ever so many neighbors would fix the problem by marrying the two into one big family so that it would be impossible to argue about which family got the next turn.


Then Prita's parents and the nearest-neighbor parents sealed themselves in a grotto to negotiate.
There they stayed and conferred and debated and meditated and argued (but more politely now that the whole tribe was watching) for two days and a night between,
and while they were away conferring, Prita fretted. She was the eldest, you see, and if they did not come to an agreement, would be the first married -- which she did not mind in principle but she had spent the last four years fueding with the nearest-neighbor boys and thought they were all rude and dullards.

On the second night her parents and the nearest neighbor parents asked for more time to confer. This gave poor Prita all the more fear that she'd be married and so she began to plan. 


TK TK Prita grows worried, leaves the crater, searches for husband to preclude possibility of marrying the dullards

TK TK sees world, meets Gorons, too young for 'em, completely unmarriageable until she turns at least 100 

TK TK Mogma, no interest in marriage

TK TK Meets two Parella alarming them both, because Parella die shortly after they\ldots{} marry.
 
On she walked until she reached the Great Sand Sea, which in those days still had a little water in it, and
there at the edge of the Great Sand Sea and the Lesser Wetter Sea, where no people live, she sat because she could not walk any further. 

TK TK meets Snake
  who was sun-red and resting himself in the lee of a rock

 ``Wherefore have you come to the desert?'' asked the viper. 

 ``O Viper, I am hiding from my mother and father, and three aunts and uncles, and five sisters, and ever so many neighbors, who want me married to a rude dullard,'' she answered ``and I have searched all over the mountains and the forest for someone else to marry so that I do not have to marry him'' and she recited the many places she had searched, and told about the Goron surveyer, and the Mogma merchant, and even the two Parella who she had asked who did not want to marry for fear of their life, and many others she had asked, and the recitation took so long that the sun had set, and the viper grew slow and sluggish but listened and heard and attended all the way through.

``A----And---wherefore wants your family an --- union with a --- dullard?'' asked the snake, although it took him a very long time to ask it.

So she explained the long argument about the chiefdom, and who should have it, and whose son should have it after that,
and the desert viper \emph{thhhhhhhhhhhhh}-d thoughtfully, and ran his red coils against themselves. 

TK TK the very chilly snake asks her to come back to his rock hibernacula, because she is warm

TK TK offers to marry her so she does not marry the dullard on condition there are no sons involved since this succession business sounds bad

TK TK she tries to explain the sons aren't the problem so much as the succession, but by then the snake was very tired indeed and Prita was just as happy with daughters, so she agrees. 

TK TK Lives in the desert with the snakes for a season returns to visit her family in the crater to find two of her sisters married and her parents still locked away arguing. Raises a huge fuss and swears off being a sheikah renounces service to Hylia (who didn't need anything anyway, on account of being frozen in amber) if it is going to be so ridiculous, joined by her sisters who also got tired of being asked to marry dullards and they all married the viper's eligible viper siblings.

TK TK Sheikah are duly embarassed by all this and revise inheritance rules to avoid another disaster.

TK TK Points covered: Gerudo: no sons by agreement with snake (Except Ganondorf, and that is another story)

TK TK Red hair which they get from their snake dad 

TK TK More of a theme to develop on the editor's notes: Presumed common linguistic origins of Gerudo and Sheikah languages, tale offer folkloric support for a common origin of the two
\end{document}